---
title: "R Notebook"
output:
  html_document:
    df_print: paged
---

```{r message=FALSE}
library(tidyverse)
library(readr)
library(lubridate)
library(roperators)
library(kableExtra)
library(ggplot2)
library(modelr)
library(purrr)
library(broom)
library(glmnet)

marathon_results_2015_1 <- read_csv("marathon_results_2015_1.csv")
marathon_results_2016_1 <- read_csv("marathon_results_2016_1.csv")
marathon_results_2017_1 <- read_csv("marathon_results_2017_1.csv")
```

# Making Wave Variable
```{r}
Marathon2015 <- marathon_results_2015_1 %>%
  mutate(Bib = as.numeric(Bib)) %>%
  mutate(Wave = ifelse((is.na(Bib) | (Bib > 0 & Bib < 101)), "Elite", 
                       ifelse(Bib >= 101 & Bib <= 7700, "One", 
                              ifelse(Bib >= 8000 & Bib <= 15600, "Two", 
                                     ifelse(Bib >= 16000 & Bib <= 23600, "Three", "Four"))))) 

Marathon2016 <- marathon_results_2016_1 %>%
  mutate(Bib = as.numeric(Bib)) %>%
  mutate(Wave = ifelse((is.na(Bib) | (Bib > 0 & Bib < 101)), "Elite", 
                       ifelse(Bib >= 101 & Bib <= 7700, "One", 
                              ifelse(Bib >= 8000 & Bib <= 15600, "Two", 
                                     ifelse(Bib >= 16000 & Bib <= 23600, "Three", "Four"))))) 



Marathon2017 <- marathon_results_2017_1 %>%
  mutate(Bib = as.numeric(Bib)) %>%
  mutate(Wave = ifelse((is.na(Bib) | (Bib > 0 & Bib < 101)), "Elite", 
                       ifelse(Bib >= 101 & Bib <= 7700, "One", 
                              ifelse(Bib >= 8000 & Bib <= 15600, "Two", 
                                     ifelse(Bib >= 16000 & Bib <= 23600, "Three", "Four"))))) 

```

# Adding Year Variable and rbinding datasets

```{r echo=FALSE}
Marathon2015$Year = 2015
Marathon2016$Year = 2016
Marathon2017$Year = 2017

MarathonAll = rbind(Marathon2015, Marathon2016, Marathon2017)

MarathonAll <- MarathonAll %>%
  rename(OfficialTime = `Official Time`)

#Converting to HR:MIN:SEC func
CONVERT.func = function(x){
  x = ((x - x %% 60) / 60) %+% ":" %+% trunc(x - (x - x %% 60)) %+% ":" %+% trunc(((x - (x - x %% 60)) -      trunc(x - (x - x %% 60))) * 60)
}

WaveMeans <- MarathonAll %>%
  group_by(Wave, Year) %>%
  summarize(mean(OfficialTime)) %>%
  spread(key = Year, value = `mean(OfficialTime)`) %>%
  arrange(`2015`)


WaveMeans$`2015` = CONVERT.func(WaveMeans$`2015`)
WaveMeans$`2016` = CONVERT.func(WaveMeans$`2016`)
WaveMeans$`2017` = CONVERT.func(WaveMeans$`2017`)

WaveMeans$`2015`[2] = "3:07:19"
WaveMeans$`2017`[3] = "3:45:07"
WaveMeans$`2017`[4] = "4:04:51"
WaveMeans$`2017`[5] = "4:45:03"


WaveMeans[6,1] = "All Runners"
WaveMeans[6,2] = "3:46:26"
WaveMeans[6,3] = "3:55:03"
WaveMeans[6,4] = "3:58:05"

kable(WaveMeans, caption = "Average Boston Marathon Times from 2015 to 2017 by Wave") %>%
  kable_styling('striped', 'bordered')



```

```{r}



Time = c(Marathon2015 %>% summarize(mean(`Official Time`)))
Marathon2016 %>% summarize(mean(`Official Time`))
Marathon2017 %>% summarize(mean(`Official Time`))


```

```{r}
MarathonAll %>% ggplot(aes(x = AgeGroup, y = OfficialTime)) + geom_boxplot(aes(color = Gender), show.legend = TRUE) + ggtitle("Distribution of Boston Marathon Times By Age Group and Sex") + labs(x = "Age Division", y = "Official Marathon Time (min)") + theme(plot.title = element_text(hjust = 0.5))
```


# Part 1: Modeling - Elastic Net Method - using Age variable

```{r}


MarathonAll1 = MarathonAll[,c("Age", "Gender", "OfficialTime", "Wave", "Year")] 
head(MarathonAll1)

y = MarathonAll1$OfficialTime
X = model_matrix(MarathonAll1,OfficialTime~.*.)[,-1]
var.names = names(X)
dim(X)
# 1st time with age instead of age group
# 2nd time with agegroup instead of age
```
```{r}
set.seed(216)
cvmod.0=cv.glmnet(y=y,x=as.matrix(X),alpha=0)
set.seed(216)
cvmod.25=cv.glmnet(y=y,x=as.matrix(X),alpha=0.25)
set.seed(216)
cvmod.5=cv.glmnet(y=y,x=as.matrix(X),alpha=0.5)
set.seed(216)
cvmod.75=cv.glmnet(y=y,x=as.matrix(X),alpha=0.75)
set.seed(216)
cvmod.1=cv.glmnet(y=y,x=as.matrix(X),alpha=1)

CV.0.ERROR=cvmod.0$cvm[which(cvmod.0$lambda==cvmod.0$lambda.1se)]
CV.25.ERROR=cvmod.25$cvm[which(cvmod.25$lambda==cvmod.25$lambda.1se)]
CV.5.ERROR=cvmod.5$cvm[which(cvmod.5$lambda==cvmod.5$lambda.1se)]
CV.75.ERROR=cvmod.75$cvm[which(cvmod.75$lambda==cvmod.75$lambda.1se)]
CV.1.ERROR=cvmod.1$cvm[which(cvmod.1$lambda==cvmod.1$lambda.1se)]

MOD.RESULT=tibble(alpha=c(0,0.25,0.5,0.75,1),
                  lambda=c(cvmod.0$lambda.1se,cvmod.25$lambda.1se,
                           cvmod.5$lambda.1se,cvmod.75$lambda.1se,
                           cvmod.1$lambda.1se),
                  CV.Error=c(CV.0.ERROR,CV.25.ERROR,CV.5.ERROR,
                             CV.75.ERROR,CV.1.ERROR))
print(MOD.RESULT)
```

```{r warning=FALSE}
best.alpha=MOD.RESULT$alpha[which.min(MOD.RESULT$CV.Error)]
best.lambda=MOD.RESULT$lambda[which.min(MOD.RESULT$CV.Error)]

best.mod=glmnet(y=y,x=as.matrix(X),nlambda=1,lambda=best.lambda,alpha=best.alpha)
best.coef=as.tibble(as.matrix(coef(best.mod)))
best.coef2=best.coef %>% 
              mutate(Parameter=c("Int",var.names)) %>%
              rename(Estimate=s0) %>%
              select(Parameter,Estimate)
nonzero.best.coef=best.coef2 %>%
                    filter(Estimate!=0)
print(nonzero.best.coef,n=1e3)

MarathonAll1$OfficialTime.hat=predict(best.mod,newx=as.matrix(X))

ggplot(MarathonAll1) +
  geom_point(aes(x=OfficialTime,y=OfficialTime.hat),color="lightskyblue2") +
  geom_abline(a=0,b=1,linetype="dashed") +
  theme_minimal() +
  ylab("Predicted Official Marathon Time") +
  xlab("Actual Marathon Time") +
  xlim(120,650)

ggplot(MarathonAll1) +
  geom_histogram(aes(x=OfficialTime-OfficialTime.hat),fill="lightskyblue2", binwidth=10) +
  theme_minimal() +
  xlab("Residuals") +
  ylab("Frequency")

# make plot of residuals compared to x
MarathonAll1 <- MarathonAll1 %>%
      mutate(Residual = OfficialTime - OfficialTime.hat)

ggplot(MarathonAll1, aes(OfficialTime, Residual)) +
      geom_ref_line(h = 0) +
      geom_point()
```

# Part 1 - Modeling using Elastic Method with Age Group

```{r}
MarathonAll2 = MarathonAll[,c("AgeGroup", "Gender", "OfficialTime", "Wave", "Year")] 
head(MarathonAll2)

y1 = MarathonAll2$OfficialTime
X1= model_matrix(MarathonAll2,OfficialTime~.*.)[,-1]
var.names = names(X1)
dim(X1)
```
```{r}
set.seed(216)
cvmod.0=cv.glmnet(y=y1,x=as.matrix(X1),alpha=0)
set.seed(216)
cvmod.25=cv.glmnet(y=y1,x=as.matrix(X1),alpha=0.25)
set.seed(216)
cvmod.5=cv.glmnet(y=y1,x=as.matrix(X1),alpha=0.5)
set.seed(216)
cvmod.75=cv.glmnet(y=y1,x=as.matrix(X1),alpha=0.75)
set.seed(216)
cvmod.1=cv.glmnet(y=y1,x=as.matrix(X1),alpha=1)

CV.0.ERROR=cvmod.0$cvm[which(cvmod.0$lambda==cvmod.0$lambda.1se)]
CV.25.ERROR=cvmod.25$cvm[which(cvmod.25$lambda==cvmod.25$lambda.1se)]
CV.5.ERROR=cvmod.5$cvm[which(cvmod.5$lambda==cvmod.5$lambda.1se)]
CV.75.ERROR=cvmod.75$cvm[which(cvmod.75$lambda==cvmod.75$lambda.1se)]
CV.1.ERROR=cvmod.1$cvm[which(cvmod.1$lambda==cvmod.1$lambda.1se)]

MOD.RESULT1=tibble(alpha=c(0,0.25,0.5,0.75,1),
                  lambda=c(cvmod.0$lambda.1se,cvmod.25$lambda.1se,
                           cvmod.5$lambda.1se,cvmod.75$lambda.1se,
                           cvmod.1$lambda.1se),
                  CV.Error=c(CV.0.ERROR,CV.25.ERROR,CV.5.ERROR,
                             CV.75.ERROR,CV.1.ERROR))
print(MOD.RESULT1)
```
```{r warning=FALSE}
est.alpha=MOD.RESULT1$alpha[which.min(MOD.RESULT1$CV.Error)]
best.lambda=MOD.RESULT1$lambda[which.min(MOD.RESULT1$CV.Error)]

best.mod=glmnet(y=y1,x=as.matrix(X1),nlambda=1,lambda=best.lambda,alpha=best.alpha)
best.coef=as.tibble(as.matrix(coef(best.mod)))
best.coef2=best.coef %>% 
              mutate(Parameter=c("Int",var.names)) %>%
              rename(Estimate=s0) %>%
              select(Parameter,Estimate)
nonzero.best.coef=best.coef2 %>%
                    filter(Estimate!=0)
print(nonzero.best.coef,n=1e3)

MarathonAll2$OfficialTime.hat=predict(best.mod,newx=as.matrix(X1))

ggplot(MarathonAll2) +
  geom_point(aes(x=OfficialTime,y=OfficialTime.hat),color="lightskyblue2") +
  geom_abline(a=0,b=1,linetype="dashed") +
  theme_minimal() +
  ylab("Predicted Official Marathon Time") +
  xlab("Actual Marathon Time") +
  xlim(120,650)

ggplot(MarathonAll2) +
  geom_histogram(aes(x=OfficialTime-OfficialTime.hat),fill="lightskyblue2", binwidth=10) +
  theme_minimal() +
  xlab("Residuals") +
  ylab("Frequency")

# make plot of residuals compared to x
MarathonAll2 <- MarathonAll2 %>%
      mutate(Residual = OfficialTime - OfficialTime.hat)

ggplot(MarathonAll2, aes(OfficialTime, Residual)) +
      geom_ref_line(h = 0) +
      geom_point() 
```

Questions:
- how to deal with horrendous residuals over x plot?
- interpreting CV.Error - can I apply it to all three situations
- future data science plans


# PART 2 - Only Runners who ran all three years

```{r}
length(unique(Marathon2015$Name))
length(unique(Marathon2016$Name))
length(unique(Marathon2017$Name))

# some non-unique names
```
```{r renaming variables to years}
Marathon2015 <- Marathon2015 %>%
  select(-Pace, -Year, -Overall, -GenderRank, -DivisionRank, -Wave, -AgeGroup, -Half, -Age, -Bib) %>%
  rename(`5K15` = `5K`,
         `10K15` = `10K`,
         `15K15` = `15K`,
         `20K15` = `20K`,
         `25K15` = `25K`,
         `30K15` = `30K`,
         `35K15` = `35K`,
         `40K15` = `40K`,
         `OfficialTime15` = `Official Time`)

Marathon2016 <- Marathon2016 %>%
  select(-Pace, -Year, -Overall, -GenderRank, -DivisionRank, -Wave, -AgeGroup, -Half, -Age, -Bib) %>%
  rename(`5K16` = `5K`,
         `10K16` = `10K`,
         `15K16` = `15K`,
         `20K16` = `20K`,
         `25K16` = `25K`,
         `30K16` = `30K`,
         `35K16` = `35K`,
         `40K16` = `40K`,
         `OfficialTime16` = `Official Time`,
         )

Marathon2017 <- Marathon2017 %>%
  select(Age, `Official Time`, Gender, Wave, Name, Country, State, City, AgeGroup)
```

BOTHYEARS.func = function(x,y) {
   for (i in seq_along(x)){ 
      if (x$Name[i] %in% y$Name) {
        z = y[i]
      }
   }
}
```{r}
Marathon2015 <- Marathon2015 %>% select(-Gender)
Marathon2016 <- Marathon2016 %>% select(-Gender)
MarathonRepeat = inner_join(Marathon2015, Marathon2016, by = c("Name", "Country", "State", "City"))

MarathonTrifecta = inner_join(MarathonRepeat, Marathon2017, by = c("Name", "Country", "State", "City"))


```

```{r}
head(MarathonTrifecta)
```
- help give sense of distribution of runners who ran all three years
- create spread variabe for 15/16
- create model

```{r}
MarathonTrifecta1 <- MarathonTrifecta %>%
  filter(!is.na(`5K15`) & !is.na(`10K15`) & !is.na(`15K15`) & !is.na(`20K15`) & !is.na(`25K15`) & !is.na(`30K15`) & !is.na(`35K15`) & !is.na(`40K15`) & !is.na(`5K16`) & !is.na(`10K16`) & !is.na(`15K16`) & !is.na(`20K16`) & !is.na(`25K16`) & !is.na(`30K16`) & !is.na(`35K16`) & !is.na(`40K16`)) %>% 
  rename(
    `OfficialTime17` = `Official Time`
  )
```

```{r tables creating distribution of gender / age group }
# Distribution of Runners Running Marathon for 3rd Consecutive Year in 2017 
# Distribution of All 2017 Marathon Runners
left_join(MarathonTrifecta %>% 
  group_by(AgeGroup) %>% 
  summarize(round(n() / length(MarathonTrifecta$Name) * 100, 2)) %>%
  rename(`Runners in 3rd Consecutive Marathon` = `round(n()/length(MarathonTrifecta$Name) * 100, 2)`,
         `Age Division` = AgeGroup) %>% 
  mutate(`Runners in 3rd Consecutive Marathon` = `Runners in 3rd Consecutive Marathon` %+% "%"),
Marathon2017 %>% 
  group_by(AgeGroup) %>%
  summarize(round(n() / length(Marathon2017$Name) * 100, 2)) %>%
  rename(`All Runners` = `round(n()/length(Marathon2017$Name) * 100, 2)`,
          `Age Division` = AgeGroup) %>%
  mutate(`All Runners` = `All Runners` %+% "%"),
by = "Age Division")

left_join(MarathonTrifecta %>% 
  group_by(Gender) %>% 
  summarize(round(n() / length(MarathonTrifecta$Name) * 100, 2)) %>%
  rename(`Runners in 3rd Consecutive Marathon` = `round(n()/length(MarathonTrifecta$Name) * 100, 2)`) %>% 
  mutate(`Runners in 3rd Consecutive Marathon` = `Runners in 3rd Consecutive Marathon` %+% "%"),

Marathon2017 %>% 
  group_by(Gender) %>%
  summarize(round(n() / length(Marathon2017$Name) * 100, 2)) %>%
  rename(`All Runners` = `round(n()/length(Marathon2017$Name) * 100, 2)`) %>%
  mutate(`All Runners` = `All Runners` %+% "%"),
by = "Gender")

# make into Kable (& shade?)
```

```{r average times for 3rd consecutive marathon}
YearMeans <- c(mean(MarathonTrifecta1$OfficialTime15), mean(MarathonTrifecta1$OfficialTime16), mean(MarathonTrifecta1$OfficialTime17))

YearMeans = CONVERT.func(YearMeans)
YearMeans[1] = "3:37:02"
YearMeans[2] = "3:45:02"
Year = c("2015", "2016", "2017")
AllRunners = c("3:46:26", "3:55:03", "3:58:05")

YearMeans <- data.frame(Year, YearMeans, AllRunners) %>%
  rename(`Runners of All 3 Marathons` = YearMeans,
         `All Runners` = AllRunners)

YearMeans

# make into kable
```

```{r manipulating intervals to be in 5K distance time}
MarathonTrifecta1$`40K15` = MarathonTrifecta1$`40K15` - MarathonTrifecta1$`35K15`
MarathonTrifecta1$`35K15` = MarathonTrifecta1$`35K15` - MarathonTrifecta1$`30K15`
MarathonTrifecta1$`30K15` = MarathonTrifecta1$`30K15` - MarathonTrifecta1$`25K15`
MarathonTrifecta1$`25K15` = MarathonTrifecta1$`25K15` - MarathonTrifecta1$`20K15`
MarathonTrifecta1$`20K15` = MarathonTrifecta1$`20K15` -MarathonTrifecta1$`15K15`
MarathonTrifecta1$`15K15` = MarathonTrifecta1$`15K15` - MarathonTrifecta1$`10K15`
MarathonTrifecta1$`10K15` = MarathonTrifecta1$`10K15` - MarathonTrifecta1$`5K15`

MarathonTrifecta1$`40K16` = MarathonTrifecta1$`40K16` - MarathonTrifecta1$`35K16`
MarathonTrifecta1$`35K16` = MarathonTrifecta1$`35K16` - MarathonTrifecta1$`30K16`
MarathonTrifecta1$`30K16` = MarathonTrifecta1$`30K16` - MarathonTrifecta1$`25K16`
MarathonTrifecta1$`25K16` = MarathonTrifecta1$`25K16` - MarathonTrifecta1$`20K16`
MarathonTrifecta1$`20K16` = MarathonTrifecta1$`20K16` - MarathonTrifecta1$`15K16`
MarathonTrifecta1$`15K16` = MarathonTrifecta1$`15K16` - MarathonTrifecta1$`10K16`
MarathonTrifecta1$`10K16` = MarathonTrifecta1$`10K16` - MarathonTrifecta1$`5K16`
```

```{r creating sd variables}
MarathonTrifecta2 <- MarathonTrifecta1 %>% mutate(stDev2015 = apply(.[(5:12)],1,sd)) %>% mutate(stDev2016 = apply(.[(14:21)],1,sd))
```

now create model
```{r}
MarathonTrifecta3 = MarathonTrifecta2[,c("OfficialTime15", "OfficialTime16", "stDev2015", "stDev2016", "Gender", "Age", "Wave", "OfficialTime17")]


y2 = MarathonTrifecta3$OfficialTime17
X2= model_matrix(MarathonTrifecta3,OfficialTime17~.*.)[,-1]
var.names = names(X2)
dim(X2)
```

```{r}
set.seed(216)
cvmod.0=cv.glmnet(y=y2,x=as.matrix(X2),alpha=0)
set.seed(216)
cvmod.25=cv.glmnet(y=y2,x=as.matrix(X2),alpha=0.25)
set.seed(216)
cvmod.5=cv.glmnet(y=y2,x=as.matrix(X2),alpha=0.5)
set.seed(216)
cvmod.75=cv.glmnet(y=y2,x=as.matrix(X2),alpha=0.75)
set.seed(216)
cvmod.1=cv.glmnet(y=y2,x=as.matrix(X2),alpha=1)

CV.0.ERROR=cvmod.0$cvm[which(cvmod.0$lambda==cvmod.0$lambda.1se)]
CV.25.ERROR=cvmod.25$cvm[which(cvmod.25$lambda==cvmod.25$lambda.1se)]
CV.5.ERROR=cvmod.5$cvm[which(cvmod.5$lambda==cvmod.5$lambda.1se)]
CV.75.ERROR=cvmod.75$cvm[which(cvmod.75$lambda==cvmod.75$lambda.1se)]
CV.1.ERROR=cvmod.1$cvm[which(cvmod.1$lambda==cvmod.1$lambda.1se)]

MOD.RESULT2=tibble(alpha=c(0,0.25,0.5,0.75,1),
                  lambda=c(cvmod.0$lambda.1se,cvmod.25$lambda.1se,
                           cvmod.5$lambda.1se,cvmod.75$lambda.1se,
                           cvmod.1$lambda.1se),
                  CV.Error=c(CV.0.ERROR,CV.25.ERROR,CV.5.ERROR,
                             CV.75.ERROR,CV.1.ERROR))
print(MOD.RESULT2)
```
```{r warning=FALSE}
est.alpha=MOD.RESULT2$alpha[which.min(MOD.RESULT2$CV.Error)]
best.lambda=MOD.RESULT2$lambda[which.min(MOD.RESULT2$CV.Error)]

best.mod=glmnet(y=y2,x=as.matrix(X2),nlambda=1,lambda=best.lambda,alpha=best.alpha)
best.coef=as.tibble(as.matrix(coef(best.mod)))
best.coef2=best.coef %>% 
              mutate(Parameter=c("Int",var.names)) %>%
              rename(Estimate=s0) %>%
              select(Parameter,Estimate)
nonzero.best.coef=best.coef2 %>%
                    filter(Estimate!=0)
print(nonzero.best.coef,n=1e3)

MarathonTrifecta3$OfficialTime17.hat=predict(best.mod,newx=as.matrix(X2))

ggplot(MarathonTrifecta3) +
  geom_point(aes(x=OfficialTime17,y=OfficialTime17.hat),color="lightskyblue2") +
  geom_abline(a=0,b=1,linetype="dashed") +
  theme_minimal() +
  ylab("Predicted 2017 Marathon Time") +
  xlab("Actual 2017 Marathon Time") +
  xlim(120,650)

ggplot(MarathonTrifecta3) +
  geom_histogram(aes(x=OfficialTime17-OfficialTime17.hat),fill="lightskyblue2", binwidth=10) +
  theme_minimal() +
  xlab("Residuals") +
  ylab("Frequency")

# make plot of residuals compared to x
MarathonTrifecta3 <- MarathonTrifecta3 %>%
      mutate(Residual = OfficialTime17 - OfficialTime17.hat)

ggplot(MarathonTrifecta3, aes(OfficialTime17, Residual)) +
      geom_ref_line(h = 0) +
      geom_point() 
```

- try without MA runners


# Part 1 - trying instead with MA Runners

```{r}
MarathonAllNonMA = MarathonAll %>%
  filter(State != "MA")

MarathonAllNonMA1 = MarathonAllNonMA[,c("Age", "Gender", "Year", "Wave", "OfficialTime")]

y3 = MarathonAllNonMA1$OfficialTime
X3= model_matrix(MarathonAllNonMA1,OfficialTime~.*.)[,-1]
var.names = names(X3)
dim(X3)
```

```{r}
set.seed(216)
cvmod.0=cv.glmnet(y=y3,x=as.matrix(X3),alpha=0)
set.seed(216)
cvmod.25=cv.glmnet(y=y3,x=as.matrix(X3),alpha=0.25)
set.seed(216)
cvmod.5=cv.glmnet(y=y3,x=as.matrix(X3),alpha=0.5)
set.seed(216)
cvmod.75=cv.glmnet(y=y3,x=as.matrix(X3),alpha=0.75)
set.seed(216)
cvmod.1=cv.glmnet(y=y3,x=as.matrix(X3),alpha=1)

CV.0.ERROR=cvmod.0$cvm[which(cvmod.0$lambda==cvmod.0$lambda.1se)]
CV.25.ERROR=cvmod.25$cvm[which(cvmod.25$lambda==cvmod.25$lambda.1se)]
CV.5.ERROR=cvmod.5$cvm[which(cvmod.5$lambda==cvmod.5$lambda.1se)]
CV.75.ERROR=cvmod.75$cvm[which(cvmod.75$lambda==cvmod.75$lambda.1se)]
CV.1.ERROR=cvmod.1$cvm[which(cvmod.1$lambda==cvmod.1$lambda.1se)]

MOD.RESULT3=tibble(alpha=c(0,0.25,0.5,0.75,1),
                  lambda=c(cvmod.0$lambda.1se,cvmod.25$lambda.1se,
                           cvmod.5$lambda.1se,cvmod.75$lambda.1se,
                           cvmod.1$lambda.1se),
                  CV.Error=c(CV.0.ERROR,CV.25.ERROR,CV.5.ERROR,
                             CV.75.ERROR,CV.1.ERROR))
print(MOD.RESULT3)
```
```{r}
est.alpha=MOD.RESULT3$alpha[which.min(MOD.RESULT3$CV.Error)]
best.lambda=MOD.RESULT3$lambda[which.min(MOD.RESULT3$CV.Error)]

best.mod=glmnet(y=y3,x=as.matrix(X3),nlambda=1,lambda=best.lambda,alpha=best.alpha)
best.coef=as.tibble(as.matrix(coef(best.mod)))
best.coef2=best.coef %>% 
              mutate(Parameter=c("Int",var.names)) %>%
              rename(Estimate=s0) %>%
              select(Parameter,Estimate)
nonzero.best.coef=best.coef2 %>%
                    filter(Estimate!=0)
print(nonzero.best.coef)

MarathonAllNonMA1$OfficialTime.hat=predict(best.mod,newx=as.matrix(X3))

ggplot(MarathonAllNonMA1) +
  geom_point(aes(x=OfficialTime,y=OfficialTime.hat),color="lightskyblue2") +
  geom_abline(a=0,b=1,linetype="dashed") +
  theme_minimal() +
  ylab("Predicted Official Marathon Time") +
  xlab("Actual Official Marathon Time") +
  xlim(120,650)

ggplot(MarathonAllNonMA1) +
  geom_histogram(aes(x=OfficialTime-OfficialTime.hat),fill="lightskyblue2", binwidth=10) +
  theme_minimal() +
  xlab("Residuals") +
  ylab("Frequency")

# make plot of residuals compared to x
MarathonAllNonMA1 <- MarathonAllNonMA1 %>%
      mutate(Residual = OfficialTime - OfficialTime.hat)

ggplot(MarathonAllNonMA1, aes(OfficialTime, Residual)) +
      geom_ref_line(h = 0) +
      geom_point() 
```



